\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-12-20 doc/publications/plos16/plos16.tex
changes to plos16.tex
add new table and add values to existing

\newcommand{\cursedforest}{{\textsc{CursedForest}}
\newcommand{\mtry}{{\texttt mtry}}
\newcommand{\ntree}{{\texttt ntree}}

@@

\marginpar{Does \cloudforest use Gini impurity or information gain? I
  thought it used infomation gain but Piotr mentions Gini}

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ {\bf Performance comparison between the different random forest implementations.}}
\begin{tabular}{|l|l|l|l|l|l||}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error}  & \bf{Runtime}  \\

@@

\multirow{5}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & randomForest (R)         & 0.05       & 24 min           \\
                                                & ranger (R)      & 0.06       & 1 min 10 seconds       \\
                                                & ranger (C++)     & 0.06       & 7 min            \\

@@

\multirow{5}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest\ & 0.06 & 4 min 2 seconds \\
                                                    & Spark ML  & 0.06 & 37 min 19 seconds \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)    & 0.06       & 4 min 30 seconds     \\
                                                    & H2O           & 0.05       & 16 hours         \\

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.04  & 19 min 19 seconds         \\
                                                    & Spark ML  & 0.04       & 8 hour 29 min        \\
                                                    & ranger (R)      &  0.05       & 28 mins         \\
\hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.02  & 56 min 43 seconds             \\
                                                    & Spark ML &    NA         &   NA               \\
                                                    & ranger (R)      & 0.03      &    3 hour 58 min     \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & XX  & 7hour 14min \\
                                                    & Spark ML & NA & NA  \\
                                                    & ranger (R)       &        NA     &        NA    \\
                                                    & ranger (C++)       &        NA     &        NA    \\
\hline

>>>>

\newcommand{\cursedforest}{\textsc{CursedForest}}
\newcommand{\mtry}{{\texttt mtry}}
\newcommand{\ntree}{{\texttt ntree}}

@@

\marginpar{Does \cursedforest use Gini impurity or information gain? I
  thought it used infomation gain but Piotr mentions Gini}

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\centering
\caption{ {\bf Performance comparison with \cursedforest\ on different subsets of the 1000 Genomes Project data.}}
\begin{tabular}{| l | r | l |}
\hline
{\bf Genome \%} & {\bf Error} & {\bf Runtime} \\ \thickhline
phase1\_chr22: 1,092 x 490,036 & 0.04 & 1 min 50 seconds \\ \hline
phase3\_chr22: 2,504 x 1,103,548 & 0.06 & 4 min 2 seconds \\ \hline
phase3\_chr1: 2,504 x 6,450,364 & 0.04 & 19 min 19 seconds \\ \hline
phase3\_chr1-3: 2,504 x 19,328,051 & 0.02 & 56 min 43 seconds \\ \hline
phase3\_chr1-22: 2,504 x 81,047,467 & 0.01 & 36 min 54 seconds \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of runtime and error for models built using \cursedforest\ on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees and was built using 130 worker nodes---each with 8GB RAM.
\end{flushleft}
\label{cursedforesttable}
\end{minipage}
\end{table}

\begin{table}[!ht]
\begin{minipage}{\textwidth}
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ {\bf Performance comparison between the different random forest implementations.}}
\begin{tabular}{| l | l | r | l |}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error}  & \bf{Runtime}  \\

@@

\multirow{5}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & randomForest (R)         & 0.05       & 24 min           \\
                                                & ranger (R)      & 0.06       & 1 min 10 seconds       \\
                                                & ranger (C++)     & 0.06       & 7 min            \\
                                                & H2O           & ??       & ??         \\

@@

\multirow{5}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest\ & 0.06 & 4 min 2 seconds \\
                                                    & Spark ML  & 0.06 & 37 min 19 seconds \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)    & 0.06       & 4 min 30 seconds     \\
                                                    & ranger (C++)     &     ??   & ??        \\
                                                    & H2O           & 0.05       & 16 hours         \\

@@

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.04  & 19 min 19 seconds         \\
                                                    & Spark ML  & 0.04       & 8 hour 29 min        \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)      &  0.05       & 28 mins         \\
                                                    & ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.02  & 56 min 43 seconds             \\
                                                    & Spark ML &    NA         &   NA               \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)      & 0.03      &    3 hour 58 min     \\
                                                    & ranger (C++)     & ??       & ??            \\
                                                    & H2O           & NA       & NA         \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & 0.01  & 3hour 16min \\
                                                    & Spark ML & NA & NA  \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)       &        NA     &        NA    \\
                                                    & ranger (C++)       &        NA     &        NA    \\
                                                    & H2O           & NA       & NA         \\
\hline
